---
title: "Developing Data Products Week 4"
author: "SitiSoraya"
date: "November 21, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is an R Markdown presentation documenting Shiny Application, called IrisApps. The application provide visualization of Iris dataset in the form of Histogram, depending on the Iris's attribute that the user select.

The IrisApps can be found at: https://sitisoraya.shinyapps.io/IrisAppsV2/

The ui.r and server.r are hosted on: https://github.com/SitiSoraya/DP-Assignment-Week-4

## The Iris dataset

```{r iris, echo = TRUE}
summary(iris)
```

## About the IrisApps

- Form of input used: radio button and slider input.
- The ui consists of two layouts: 
    - the sidebar panel, consists of radio buttons representing Iris's attributes, where the user can select to view in the form of histogram. The sidebar panel also consists of a slider input to specify bins range.
    - the main panel shows the generated histogram.

## ui.r code
library(shiny)

ui <- fluidPage(
    
    titlePanel("IrisApps"),
    
    sidebarLayout(
        sidebarPanel(
            helpText("This Apps provide visualization of Iris dataset 
            in the form of Histogram, depending on the Iris's attribute 
            that the user select."),
            radioButtons("option", "Choose Iris attribute:",
            list("Sepal.Length"='a', "Sepal.Width"='b', "Petal.Length"='c',
            "Petal.Width"='d')),
            sliderInput("bins", "Specify the bins range:", min = 1, max = 50, 
            value = 30)
        ),
    mainPanel(mainPanel(plotOutput("distPlot")) )))

```{r}
library(shiny)

# Define ui for IrisApps that draws a histogram
ui <- fluidPage(
    
    titlePanel("IrisApps"),
    
    # Sidebar with radio buttons for attribute option and a slider input for bins range 
    sidebarLayout(
        sidebarPanel(
            helpText("This Apps provide visualization of Iris dataset in the form of Histogram, depending on the Iris's attribute that the user select."),
            
            radioButtons("option", "Choose Iris attribute:", list("Sepal.Length"='a', "Sepal.Width"='b', "Petal.Length"='c', "Petal.Width"='d')),
            sliderInput("bins",
                        "Specify the bins range:",
                        min = 1,
                        max = 50,
                        value = 30)
        ),
        
        # Visualization of Iris Dataset through Histogram
        mainPanel(
            mainPanel(plotOutput("distPlot"))
        )
    )
)
```

## server.r code
server <- function(input, output) {
    
    output$distPlot <- renderPlot({
        if(input$option=='a'){       
            i<-1     }     
        if(input$option=='b'){       
            i<-2     }     
        if(input$option=='c'){       
            i<-3     }     
        if(input$option=='d'){       
            i<-4     }
        
        x    <- iris[, i] 
        bins <- seq(min(x), max(x), length.out = input$bins + 1)
        
        hist(x, main = "Histogram of Iris Dataset", xlab = "Iris Attribute", 
        ylab = "Frequency", breaks = bins, col = 'blue', border = 'white')
    }) }

```{r}
server <- function(input, output) {
    
    output$distPlot <- renderPlot({
        if(input$option=='a'){       
            i<-1     }     
        if(input$option=='b'){       
            i<-2     }     
        if(input$option=='c'){       
            i<-3     }     
        if(input$option=='d'){       
            i<-4     }
        
        # generate bins based on input$bins from ui.R
        x    <- iris[, i] 
        bins <- seq(min(x), max(x), length.out = input$bins + 1)
        
        # draw the histogram with the specified bins range
        hist(x, main = "Histogram of Iris Dataset", xlab = "Iris Attribute", ylab = "Frequency", breaks = bins, col = 'blue', border = 'white')
    })
}
```