---
title: "Developing Data Products Week 4"
author: "SitiSoraya"
date: "November 20, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is an R Markdown presentation documenting Shiny Application, called IrisApps. The application provide visualization of Iris datasets in the form of Histogram, depending on the Iris's attributes (i.e. column of Iris datasets) that the user select.

The IrisApps can be found at: https://sitisoraya.shinyapps.io/IrisApps/

The ui.r and server.r are hosted on: https://github.com/SitiSoraya/DP-Assignment-Week-4

## The Iris datasets

```{r iris, echo = TRUE}
summary(iris)
```

## About the IrisApps

- Form of input used: radio button and slider input.
- The ui consists of two layouts: 
    - the sidebar panel, consists of radio buttons representing Iris's attributes, where the user can select to view in the form of histogram. The sidebar panel also consists of a slider input for number of bins.
    - the main panel shows the generated histogram.

## ui.r code
library(shiny)

ui <- fluidPage(
    
    titlePanel("Iris datasets"),
     
    sidebarLayout(
        sidebarPanel(radioButtons("option", "Column of iris dataset:", 
        list("Sepal.Length"='a', "Sepal.Width"='b', "Petal.Length"='c', 
        "Petal.Width"='d')),
            sliderInput("bins",
                        "Number of bins:", min = 1, max = 50, value = 30)
        ),
        
        mainPanel(
            mainPanel(plotOutput("distPlot")) )))

```{r}
library(shiny)

# Define UI for application that draws a histogram
ui <- fluidPage(
    
    # Application title
    titlePanel("Iris datasets"),
    
    # Sidebar with a slider input for number of bins 
    sidebarLayout(
        sidebarPanel(radioButtons("option", "Column of iris dataset:", list("Sepal.Length"='a', "Sepal.Width"='b', "Petal.Length"='c', "Petal.Width"='d')),
            sliderInput("bins",
                        "Number of bins:",
                        min = 1,
                        max = 50,
                        value = 30)
        ),
        
        # Show a plot of the generated distribution
        mainPanel(
            mainPanel(plotOutput("distPlot"))
        )
    )
)
```

## server.r code
server <- function(input, output) {
    
    output$distPlot <- renderPlot({
        if(input$option=='a'){       
            i<-1     }     
        if(input$option=='b'){       
            i<-2     }     
        if(input$option=='c'){       
            i<-3     }     
        if(input$option=='d'){       
            i<-4     }
        
        x    <- iris[, i] 
        bins <- seq(min(x), max(x), length.out = input$bins + 1)
        
        hist(x, breaks = bins, col = 'darkgray', border = 'white')
    }) }

```{r}
server <- function(input, output) {
    
    output$distPlot <- renderPlot({
        if(input$option=='a'){       
            i<-1     }     
        if(input$option=='b'){       
            i<-2     }     
        if(input$option=='c'){       
            i<-3     }     
        if(input$option=='d'){       
            i<-4     }
        
        # generate bins based on input$bins from ui.R
        x    <- iris[, i] 
        bins <- seq(min(x), max(x), length.out = input$bins + 1)
        
        # draw the histogram with the specified number of bins
        hist(x, breaks = bins, col = 'darkgray', border = 'white')
    })
}
```